SULI Report!

### 2015-08-17 doc/suli-report-swe.tex
Broke up the first sentence of the introduction into smaller pieces. Small formatting changes to the second paragraph of the introduction. #81

In a universe teeming with galaxies and light, it came as a shock to 20th century astronomers that most of the mass in the universe is in fact dark. The `normal' matter made of atoms that we interact with in everyday life, called baryonic matter, only accounts for (20\%?) of the mass in the observable universe, and only (4.9\%?) of the mass-energy content of the universe (cite L-CDM). While this claim sounds bizarre, there has been an abundance of indirect evidence in recent decades for the existence of dark matter including the flattening of galaxy rotation curves (cite), the existence of baryonic acoustic oscillations (cite), and anisotropies in the cosmic microwave background (cite).

One of the most successful probes of dark matter has been gravitational lensing. The path of light from distant `background' galaxies is bent when traveling through regions of space containing large amounts of `foreground' mass. The process is described by Einstein's theory of general relativity, but simply put – the more mass, the more light bends. Light from different origins in a background galaxy are subject to different bending which results in a distortion of the galaxy image. As the foreground mass is known to be largely dark matter, gravitational lensing supplies a direct constraint on the mass of dark matter in that region.

>>>>

In a universe teeming with galaxies and light, it came as a shock when 20\textsuperscript{th} century astronomers unexpectedly discovered that most of the mass in the universe is in fact dark; the `normal' matter made of atoms that we interact with in everyday life, called baryonic matter, only accounts for (20\%?) of the mass in the observable universe. The remaining mass takes the form of an exotic dark matter that does not absorb or emit light, rendering it invisible to our telescopes. While this claim sounds bizarre, there has been an abundance of indirect evidence in recent decades for the existence of dark matter including the flattening of galaxy rotation curves (cite), the existence of baryonic acoustic oscillations (cite), and anisotropies in the cosmic microwave background (cite).

One of the most successful probes of dark matter has been gravitational lensing. The path of light from distant `background' galaxies is bent when traveling through regions of space containing large amounts of `foreground' mass. The process is described by Einstein's general theory of relativity, but simply put -- the more mass, the more light bends. Light from different origins in a background galaxy are subject to different bending which results in a distortion of the galaxy image. As the foreground mass is known to be largely dark matter, gravitational lensing supplies a direct constraint on the mass of dark matter in that region.
